\subsubsection{TPTP.}
Two subsets of the TPTP problem library~\cite{Sut17} are used. The first is a
737-problem provable subset (FOF/THM), restricted to problems with 0--50 input
formulae, 0--150 atoms, and no equality or arithmetic. The second is a
204-problem counter-satisfiable subset (FOF/CSA) drawn from the same
complexity bounds, in which each problem is known to have no proof because
its negation is satisfiable. TPTP was chosen because it provides a large
number of problems with known satisfiability status across diverse mathematical
domains, with well-established filters (such as the TPTP2T tool) that make it
straightforward to select subsets matching the implemented fragment. The two
subsets together test both sides of the prover: the ability to find proofs and
the ability to exhaust the search space and report \textit{NotProvable}.

\subsubsection{FOLIO.}
The FOLIO dataset~\cite{han2024folio} consists of natural-language reasoning
problems in which human-authored premises about everyday scenarios are
formalised as FOF axioms and a conclusion is posed as a conjecture. The
validation split, comprising 280 generated FOF files (140 entailment/refutation
pairs), is included to evaluate the prover on a dataset with less controlled
filtering than TPTP, testing whether its behaviour generalises to
semantically grounded, natural-language-derived problems.

\subsubsection{Synthetic.}
To complement the above, 202 synthetic FOF problems in TPTP format were
generated programmatically using a purpose-built Python script
(\texttt{scripts/generate\_fof\_benchmarks.py}), distributed one per file
across four tiers: \emph{easy} (32), \emph{medium} (60), \emph{hard} (60),
and \emph{expert} (50). Synthetic problems were used to provide direct control
over difficulty, since both proof depth and distractor count are fixed by
construction for every problem.

Four problem families are used. \textbf{Implication chains} consist of a
ground fact $p_0(a)$, a sequence of $n$ universally quantified steps
$\forall X.\,(p_i(X)\Rightarrow p_{i+1}(X))$, and the conjecture $p_n(a)$;
the proof requires $n$ sequential $\forall L$ instantiations with the
constant $a$.  $d$ structurally identical but irrelevant \emph{distractor}
axioms of the same form are added, increasing the number of applicable
quantifier rules at each step without contributing to any proof.  Unprovable
variants remove one link from the chain, leaving an irreparable gap.
\textbf{Syllogisms} encode a fixed class hierarchy
(\texttt{entity}$\to$\texttt{organism}$\to\cdots\to$\texttt{teacher}) with
a ground instance for one individual; unprovable variants change the
individual in the conjecture to one for whom no ground fact exists.
\textbf{Transitivity chains} provide a single binary transitivity axiom
$\forall X,Y,Z.\,(\mathit{rel}(X,Y)\wedge\mathit{rel}(Y,Z)\Rightarrow
\mathit{rel}(X,Z))$ together with a sequence of ground edge facts; unlike
implication chains, the proof requires \emph{repeated reuse} of the same
axiom across different instantiations. Unprovable variants ask for a node
unreachable by the given edges. \textbf{Quantifier alternation} problems
are single-formula conjectures testing classical $\forall/\exists$ theorems
and non-theorems: Drinker's paradox~\cite{smullyan1978}, Russell's
diagonal~\cite{russell1902}, the converse Barcan formula~\cite{barcan1946},
Pelletier~18~\cite{pelletier1986}, and the (unprovable) forward Barcan
formula~\cite{barcan1946} and $(\exists X.\,p(X))\Rightarrow(\forall
Y.\,p(Y))$ inferences.

Difficulty scales across tiers by simultaneously increasing proof depth
($n\in[2,15]$) and distractor count ($d\in[0,14]$).
