\section{Discussion and Conclusion}

\subsection{Discussion}

The three-engine design allows gains to be attributed directly: \texttt{id}
adds only iterative deepening to the naive baseline, and \texttt{priority-id}
adds only the six-class priority schedule on top of \texttt{id}, with all
other code shared. Across all three datasets, \texttt{id} decides 60 more
problems than \texttt{naive} (299 vs.\ 239), and \texttt{priority-id}
decides a further 22 more than \texttt{id} (321 vs.\ 299). Iterative
deepening therefore accounts for 60 of the 82 additional decisions over the
baseline (73\,\%), and the priority schedule for the remaining 22 (27\,\%).

The FOLIO results require a more careful reading. \texttt{id} and
\texttt{naive} both decide 57 FOLIO problems, so iterative deepening
produces no net gain in decided count on that dataset. Crucially, no
problem changes its decided outcome between engines: every \textit{Provable}
decision remains \textit{Provable} and every \textit{NotProvable} decision
remains \textit{NotProvable} whenever it is reached. What iterative
deepening changes is which problems get decided at all: it converts 11
naive-timeout problems to \textit{Provable} decisions, but simultaneously
causes 5 naive-\textit{Provable} problems to time out (restarts spend the
step budget before those proof branches close) and renders 6
naive-\textit{NotProvable} problems undecided (restarts cannot exhaust the
search space within the budget). The net is zero. All 9 additional FOLIO
decisions come from \texttt{priority-id}, which preserves all 23 of
\texttt{naive}'s \textit{NotProvable} decisions intact, converts 9
naive-timeout problems to \textit{Provable}, and converts a further 5
timeouts and unknowns to \textit{NotProvable}, while losing only 5
\textit{Provable} decisions to timeout.

Across all datasets, roughly 70\,\% of problems remain undecided, with
timeouts dominating over \textit{Unknown} outcomes. This indicates the
bottleneck is search-space width rather than raw time, and that sharper
rule-selection heuristics would have more impact than a larger resource
budget.

\subsection{Limitations}

\textbf{Timing reliability.} Wall-clock timing at a 1{,}000\,ms timeout is
subject to OS scheduling jitter on the host (Windows~11); individual solve
times below approximately 50\,ms are not reliably comparable across runs.
The primary metric for this experiment is the number of problems decided,
which is deterministic given fixed resource bounds.

\textbf{TPTP difficulty ceiling.} Every problem solved by any engine has a
TPTP difficulty rating of at most 0.10 (as recorded in the \texttt{\%
Rating} field of each problem file); no problem rated above 0.10 is decided
by any engine. The 139 problems in the provable subset with rating above
0.10 are uniformly unsolved, indicating the prover is confined to the
easiest tier of the TPTP benchmark.

\textbf{Recursive depth bound.} The backward search is implemented as
direct Rust recursion with a software depth counter, bounded at 128 rule
applications (\texttt{max\_depth} in \texttt{ProofOptions}). Any proof
requiring more than 128 sequential rule applications returns
\textit{Unknown} regardless of time or step budget. Proofs requiring
deeper search are therefore structurally unreachable under the current
implementation.

\textbf{Comparison with mature systems.} The prover is not competitive with
connection-based systems (leanCoP~\cite{otten2003leancop},
leanTAP~\cite{beckert1995leantap}) or saturation-based systems
(Vampire~\cite{kovacs2013vampire}, E~\cite{schulz2002E}), which use
fundamentally more efficient proof strategies and decades of engineering.
This work is a controlled study of targeted refinements to a textbook
sequent calculus, not a production ATP system.

\subsection{Improvements}

\textbf{Lemma sharing.} Iterative deepening re-traverses all branches at
each depth increment. Caching closed subgoals across iterations would
amortise this re-traversal cost without altering the proof strategy.

\textbf{Smarter witness selection.} The reusable-quantifier classes
currently enumerate witnesses by position in the sequent. Unification-based
instantiation, as in leanTAP~\cite{beckert1995leantap}, selects witnesses
guided by the conjecture structure, dramatically reducing the branching
factor at quantifier steps.

\textbf{Alternative proof strategies.} The long-term path to competitive
performance is a structural change away from backward sequent search.
Connection-based methods~\cite{otten2003leancop} and saturation-based
methods~\cite{kovacs2013vampire,schulz2002E} have demonstrated orders-of-magnitude
better scaling on the TPTP benchmark and represent the natural next step
beyond the refinements studied here.

\subsection{Conclusion}

The principal lesson of this study is that small, principled changes to the
rule-application order of a textbook sequent calculus produce
disproportionate improvements in practical solve rate. Iterative deepening
and the six-class LK$'$ priority schedule together raise the number of
decided problems from 239 to 321 across three diverse datasets, without any
change to the underlying proof calculus or the addition of heavyweight
machinery. The bottleneck that remains is search-space width, and the
natural successors to this work are unification-based witness selection and
a transition to connection-based or saturation-based proof strategies.

\subsubsection{Data Availability.}
Source code, benchmark scripts, and the SQLite database backing every
figure in this paper are available at the project repository on GitHub.
